### 2018-06-28 paper/2-background.tex
Label Bazel as dynamic

\begin{table}[h]
\smaller
\centering
\begin{tabular}{l||l|l||l|c|c|c}
\hline
$\!$Build system$\!$& Persistent build information & Algorithm   & Dependencies   & Minimal & Cutoff & Cloud$\!$\\\hline
$\!$\Make       $\!$& File modification times      & Topological & Static         & Yes     & No     & No   $\!$\\
$\!$\Excel      $\!$& Dirty cells, calc chain      & Restarting  & Dynamic        & No      & No     & No   $\!$\\
$\!$\Shake      $\!$& Previous dependency graph    & Suspending  & Dynamic        & Yes     & Yes    & No   $\!$\\
$\!$\Bazel      $\!$& Cloud cache, command history & Restarting  & Static$^{(*)}$ & No      & Yes    & Yes  $\!$\\\hline
\hline
\end{tabular}
\vspace{0.5mm}
\caption{Summary of build system differences; $^{(*)}$predefined build rules can
have dynamic dependencies.\label{tab-summary}}
\vspace{-6mm}
\end{table}

In this paper we elucidate which build system properties are consequences of
specific implementation choices (stored metadata and task scheduling algorithm),
and how one can obtain new build systems with desired properties by recombining
parts of existing implementations. As a compelling example, we demonstrate how
to combine the advantages of \Shake and \Bazel in a cloud build system with
dynamic dependencies, see~\S\ref{sec-implementation-cloud}.

>>>>

\begin{table}[h]
\smaller
\centering
\begin{tabular}{l||l|l||l|c|c|c}
\hline
$\!$Build system$\!$& Persistent build information & Algorithm   & Dependencies    & Minimal & Cutoff & Cloud$\!$\\\hline
$\!$\Make       $\!$& File modification times      & Topological & Static          & Yes     & No     & No   $\!$\\
$\!$\Excel      $\!$& Dirty cells, calc chain      & Restarting  & Dynamic         & No      & No     & No   $\!$\\
$\!$\Shake      $\!$& Previous dependency graph    & Suspending  & Dynamic         & Yes     & Yes    & No   $\!$\\
$\!$\Bazel      $\!$& Cloud cache, command history & Restarting  & Dynamic$^{(*)}$ & No      & Yes    & Yes  $\!$\\\hline
\hline
\end{tabular}
\vspace{0.5mm}
\caption{Summary of build system differences; $^{(*)}$used-defined build rules
cannot have dynamic dependencies.\label{tab-summary}}
\vspace{-6mm}
\end{table}

In this paper we elucidate which build system properties are consequences of
specific implementation choices (stored metadata and task scheduling algorithm),
and how one can obtain new build systems with desired properties by recombining
parts of existing implementations. As a compelling example,
in~\S\ref{sec-implementation-cloud} we demonstrate how to combine the advantages
of \Shake and \Bazel.
